EE454 Project 1 Report

### 2015-09-24 p1/report/latex/draft.tex
fixed quote direction

Given a set of images where each image falls into a class, the neural net should be able to take the image as input and label the image.

@@

\section{Further Exploration}
\subsection{Test Cases}
To test the robustness/accuracy of the training outside of the given data set, additional test images were gathered and fed into the CNN.  Images were rescaled to thumbnail size (32x32x3) with the Matlab command
\begin{lstlisting}
thumbnail = imresize(img, [32 32]);
\end{lstlisting}

\noindent
110 images total were collected; 100 fell into the preexisting image classes, 10 contained scenes not falling into any preexisting class.  Running these new 10 images through the CNN yielded the following results:\\

@@

~\\~\\
\noindent
All of the exploratory images we used were either taken by us or were taken from Google Images. The code we used to read in the exploratory images can be found in 'getAllFiles.m' and 'getTrueClass.m'. We produced the results above by running the 10 images through the function found in 'NeuralNet.m' and classifying the images by assigning the image the class associated with the highest probability. The classification process was done manually.

>>>>

Given a set of images where each image falls into a class, the neural net should be able to take the image as input and label the image.  The test images provided also have ground-truth classifications; so, we can compare the results of the CNN with the ground truth labels to obtain a measure of accuracy.

@@

\section{Further Exploration}
\subsection{Test Cases}
To test the robustness/accuracy of the training outside of the given data set, additional test images were gathered and fed into the CNN.  Images were rescaled to thumbnail size (32x32x3) with the Matlab command
\begin{lstlisting}
thumbnail = imresize(img, [32 32]);
\end{lstlisting}
\noindent
110 images total were collected; 100 fell into the preexisting image classes, 10 contained scenes not falling into any preexisting class.  Running these new 10 images through the CNN yielded the following results:\\

@@

~\\~\\
\noindent
All of the exploratory images we used were either taken by us or were taken from Google Images. The code we used to read in the exploratory images can be found in `getAllFiles.m' and `getTrueClass.m'. We produced the results above by running the 10 images through the function found in `NeuralNet.m' and classifying the images by assigning the image the class associated with the highest probability. The classification process was done manually.
